### 2019-07-10 2-Chapters/4-Chapter/IEEE_WCNC_2019__DemoICT.git/main.tex
Using https://sylvainhalle.github.io/textidote/

This PoC implements an IoT network the following way: one base station, one or several intelligent (\emph{i.e.}, learning) devices, embedding the proposed solution,
and a traffic generator that emulates radio interference from many other devices.
Intelligent devices communicate with the base station with a wireless ALOHA-based protocol with acknowledgements, which does not require any specific overhead for the learning.
%
Similarly to the previous section, network access is modelled as a discrete sequential decision making problem, and using the framework and algorithms from MAB learning, we show that intelligent devices can improve their access rate to the network, by using low complexity and decentralized algorithms, such as \UCB{} and Thompson Sampling.
%
This solution could be added in a straightforward and costless manner in most IoT networks, such as LoRaWAN networks, just by adding this feature at the higher level of the MAC layer, in all or only some of the devices, without any modification on the network side, and no signalling overhead for the devices.

>>>>

This PoC implements an IoT network the following way: one base station, one or several intelligent (\ie, learning) devices, embedding the proposed solution,
and a traffic generator that emulates radio interference from many other devices.
Intelligent devices communicate with the base station with a wireless ALOHA-based protocol with acknowledgements, which does not require any specific overhead for the learning.
%
Similarly to the previous section, network access is modelled as a discrete sequential decision making problem, and using the framework and algorithms from MAB learning, we show that intelligent devices can improve their access rate to the network, by using low complexity and decentralized algorithms, such as \UCB{} and Thompson Sampling.
%
This solution could be added in a straightforward and costless manner in most IoT networks, such as LoRaWAN networks, just by adding this feature at the higher level of the MAC layer, in all or only some of the devices, without any modification on the network side, and no signalling overhead for the devices.

### 2019-07-10 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits.tex
Using https://sylvainhalle.github.io/textidote/

\begin{smallproof}
  Recall that we want to upper bound
  $ \ref{eq:5:term2} : = \sum_{k \in \Mbest} (\mu_k - \mu_{M*}) \left(T - \E_{\mu}[N_k(T)]\right)$.
  First, we observe that, for all $k\in \Mbest$,
  % \begin{eqnarray*}
    $T - \E_{\mu}[N_k(T)] \leq T - \E_{\mu}\left[\sum_{t=1}^T \indic(\exists j : A^j(t) = k)\right] = \E_{\mu}\left[\sum_{t=1}^T \indic(\forall j, A_j(t) \neq k)\right] = \E_{\mu}\left[\sum_{t=1}^T \indic(k \notin \widehat{S}_t)\right]$,
  % \end{eqnarray*}
  where we denote by $\widehat{S}_t = \{A^j(t), j \in [M]\}$ the set of selected arms at time $t$ (with no repetition). With this notation one can write
  \begin{eqnarray*}
  \ref{eq:5:term2} & \leq & (\mu_1 - \mu_{M^*})  \sum_{k \in \Mbest} \left(T - \E_{\mu}[N_k(T)]\right) \leq  (\mu_1 - \mu_{M^*})  \E_{\mu}\left[\sum_{k \in \Mbest} \sum_{t = 1}^T \indic(k \notin \widehat{S}_t)\right] \\
  & = &  (\mu_1 - \mu_{M^*})  \E_{\mu}\left[ \sum_{t = 1}^T \sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)\right].
  \end{eqnarray*}
  The quantity $\sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)$ counts the number of optimal arms that have not been selected at time $t$. For each mis-selection of an optimal arm, there either exists a sub-optimal arm that has been selected, or an arm in $\Mbest$ on which a collision occurs. Hence
  \[\sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t) = \sum_{k \in \Mbest}\indic(C_k(t)) + \sum_{k \in \Mworst} \indic(\exists j : A^j(t) = k),\]
  which yields
  \[\E_{\mu}\left[ \sum_{t = 1}^T \sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)\right] \leq \sum_{k \in \Mbest}\E_{\mu}\left[\cC_k(T)\right] + \sum_{k \in \Mworst} \E_{\mu}\left[N_k(T)\right]\]
  and Lemma~\ref{lem:5:1stUpperBound} follows.
\end{smallproof}

>>>>

\begin{smallproof}
  Recall that we want to upper bound
  $ \ref{eq:5:term2} \eqdef \sum_{k \in \Mbest} (\mu_k - \mu_{M*}) \left(T - \E_{\mu}[N_k(T)]\right)$.
  First, we observe that, for all $k\in \Mbest$,
  % \begin{eqnarray*}
    $T - \E_{\mu}[N_k(T)] \leq T - \E_{\mu}\left[\sum_{t=1}^T \indic(\exists j : A^j(t) = k)\right] = \E_{\mu}\left[\sum_{t=1}^T \indic(\forall j, A_j(t) \neq k)\right] = \E_{\mu}\left[\sum_{t=1}^T \indic(k \notin \widehat{S}_t)\right]$,
  % \end{eqnarray*}
  where we denote by $\widehat{S}_t = \{A^j(t), j \in [M]\}$ the set of selected arms at time $t$ (with no repetition). With this notation one can write
  \begin{eqnarray*}
  \ref{eq:5:term2} & \leq & (\mu_1 - \mu_{M^*})  \sum_{k \in \Mbest} \left(T - \E_{\mu}[N_k(T)]\right) \leq  (\mu_1 - \mu_{M^*})  \E_{\mu}\left[\sum_{k \in \Mbest} \sum_{t = 1}^T \indic(k \notin \widehat{S}_t)\right] \\
  & = &  (\mu_1 - \mu_{M^*})  \E_{\mu}\left[ \sum_{t = 1}^T \sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)\right].
  \end{eqnarray*}
  The quantity $\sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)$ counts the number of optimal arms that have not been selected at time $t$. For each mis-selection of an optimal arm, there either exists a sub-optimal arm that has been selected, or an arm in $\Mbest$ on which a collision occurs. Hence
  \[\sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t) = \sum_{k \in \Mbest}\indic(C_k(t)) + \sum_{k \in \Mworst} \indic(\exists j : A^j(t) = k),\]
  which yields
  \[\E_{\mu}\left[ \sum_{t = 1}^T \sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)\right] \leq \sum_{k \in \Mbest}\E_{\mu}\left[\cC_k(T)\right] + \sum_{k \in \Mworst} \E_{\mu}\left[N_k(T)\right]\]
  and Lemma~\ref{lem:5:1stUpperBound} follows.
\end{smallproof}

### 2019-07-10 2-Chapters/5-Chapter/chapter5.tex
Using https://sylvainhalle.github.io/textidote/

The second idea comes from \cite{Rosenski16}, and suppose to know beforehand both the horizon $T$ and a certain measure of the difficulty of the problem (\ie, a lower bound on the minimal gap between two means).
If all the $M$ players start to play for a long enough time $T_0$ uniformly at random among all the $K$ arms, then the (expected) number of collisions observed $\E[\cC^j_{T_0}]$ by any player $j$ is a (relatively simple) function of $M$. By knowing $K$ and $T_0$ and if all players use the same mechanism, then they can invert the formula to obtain the most likely estimate of $M$ which explained the observations of $\cC^j_{T_0}$ collisions.
This second approach works empirically very fine, but it requires a fine tuning of the stopping time $T_0$.
Rosenski et al. studies the performance of their algorithm with high-probability bounds \cite{Rosenski16}, and the tuning of $T_0$ they propose depends on prior knowledge on the problem.
%
For this reason, we are not fond of this approach, as this hypothesis is quite unrealistic if one wants to apply this kind of algorithms for real-world wireless networks.
We note that all the following works assume some sort of prior knowledge on the difficulty of the problem:
\cite{kumar2017channel,KumarYadav2018,SawantKumar2018,JoshiKumar2018,DarakHanawal18,KumarDarak2019,Tibrewal2019}.

>>>>

The second idea comes from \cite{Rosenski16}, and suppose to know beforehand both the horizon $T$ and a certain measure of the difficulty of the problem (\ie, a lower bound on the minimal gap between two means).
If all the $M$ players start to play for a long enough time $T_0$ uniformly at random among all the $K$ arms, then the (expected) number of collisions observed $\E[\cC^j_{T_0}]$ by any player $j$ is a (relatively simple) function of $M$. By knowing $K$ and $T_0$ and if all players use the same mechanism, then they can invert the formula to obtain the most likely estimate of $M$ which explained the observations of $\cC^j_{T_0}$ collisions.
This second approach works empirically very fine, but it requires a fine tuning of the stopping time $T_0$.
J. Rosenski and O. Shamir and L. Szlak study the performance of their algorithm with high-probability bounds \cite{Rosenski16}, and the tuning of $T_0$ they propose depends on prior knowledge on the problem.
%
For this reason, we are not fond of this approach, as this hypothesis is quite unrealistic if one wants to apply this kind of algorithms for real-world wireless networks.
We note that all the following works assume some sort of prior knowledge on the difficulty of the problem:
\cite{kumar2017channel,KumarYadav2018,SawantKumar2018,JoshiKumar2018,DarakHanawal18,KumarDarak2019,Tibrewal2019}.
